### 2022-03-08 manuscript.tex
tuba2 [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/188382bd4c0e8176aaab45f4a32f8536d20901a0.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/188382bd4c0e8176aaab45f4a32f8536d20901a0/checks
https://github.com/scherzerthesis/thesis/actions/runs/1952517789

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/b29421e075710adb5fe500990928b63a6ce51d6f/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/b29421e075710adb5fe500990928b63a6ce51d6f}{scherzerthesis/thesis@b29421e}
on March 8, 2022.

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/188382bd4c0e8176aaab45f4a32f8536d20901a0/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/188382bd4c0e8176aaab45f4a32f8536d20901a0}{scherzerthesis/thesis@188382b}
on March 8, 2022.

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}
